A generic and fast C++ optimization framework

### 2017-10-19 paper.tex
Extend conclusion

However, the current landscape of optimization frameworks for machine learning
is not particularly comprehensive.  A variety of tools such as
Caffe \cite{jia2014caffe},
% mxnet ??
TensorFlow \cite{abadi2016tensorflow},
and
Keras \cite{chollet2015}
have optimization frameworks, but they are limited to SGD-type optimizers and
only are able to optimize deep neural networks or related structures.  Thus
expressing arbitrary machine learning objective functions can be difficult or in
some cases not possible.  Other libraries, like
% Shogun \cite{shogun}
%and
scikit-learn \cite{pedregosa2011scikit},
do have optimizers implementation, but generally not in a coherent framework and
often the implementations may be specific to an individual machine learning
algorithm.  At a higher level, many programming languages may have generic
optimizers, like SciPy \cite{jones2014scipy} and MATLAB, but typically these
optimizers are not suitable for large-scale machine learning tasks where, e.g.,
calculating the full gradient of all of the data may not be feasible.

@@

We have identified that the support for generic and robust optimization is not
currently available in most machine learning toolkits, and acted upon this
observation to provide an easy framework for both implementing new optimizers
and new objective functions to be optimized inside of the {\bf mlpack} machine
learning library.  This supports a

>>>>

However, the current landscape of optimization frameworks for machine learning
is not particularly comprehensive.  A variety of tools such as
Caffe \cite{jia2014caffe},
% mxnet ??
TensorFlow \cite{abadi2016tensorflow},
and
Keras \cite{chollet2015}
have optimization frameworks, but they are limited to SGD-type optimizers and
are only able to optimize deep neural networks or related structures.  Thus
expressing arbitrary machine learning objective functions can be difficult or in
some cases not possible.  Other libraries, like
% Shogun \cite{shogun}
%and
scikit-learn \cite{pedregosa2011scikit},
do have optimizers implementation, but generally not in a coherent framework and
often the implementations may be specific to an individual machine learning
algorithm.  At a higher level, many programming languages may have generic
optimizers, like SciPy \cite{jones2014scipy} and MATLAB, but typically these
optimizers are not suitable for large-scale machine learning tasks where, e.g.,
calculating the full gradient of all of the data may not be feasible.

@@

We have identified that the support for generic and robust optimization is not
currently available in most machine learning toolkits, and acted upon this
observation to provide an easy framework for both implementing new optimizers
and new objective functions to be optimized inside of the {\bf mlpack} machine
learning library.

The framework provided by {\bf mlpack} supports a wide array of special cases,
and offers specialized algorithms that outperform their classic generic
alternatives.
